---
title: "scRNA-seq"
output: html_document
date: "2025-12-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
Fig 2A: 
Goal: identify 8CLCs in naive hESC cultures
Cell types: control vs LINE1 KD RSeT + DT hESCs


```{r setup}
library(Seurat)
library(dplyr)
library(ggplot2)
library(GEOquery)
```

## Load Data
GEO data structure:
1) Platform (GPL): Describes array design, probes, or detectable elements
2) Sample (GSM): Contains individual experiment measurements
3) Series (GSE): Groups related samples together, typically representing a complete study

1st error: timeout when downloading large datasets from GEO (11.3 GB). Suggested solution: download manually from GEO website and load locally.

Due to time constraints, I will analyze "D:\Integrated Sciences\bioinfo\GEO data\GSE232939-GPL16791_series_matrix.txt.gz" 1st.
```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
